Submission outcomes by author and gatekeeper characteristics

### 2019-02-25 figures/gatekeeper_author_outcomes/gatekeeper_author_outcomes.Rmd
edited homegeny figures (current fig 5), added panel labels and other minor tweaks

# converts a provided p-value into a representation that is easier to visualize
sig2ast <- function(p) { ifelse(p <= 0.0001, "****", 
                                ifelse(p <= 0.001, "***", 
                                       ifelse(p <= 0.01, "**", 
                                              ifelse(p <= 0.05, "*", 
                                                     ifelse(p < 0.1, ".", "ns")
                                              )
                                       )
                                )
                          )
}

@@

# Construct the final plot
gender_homophily <- data_homophily %>% 
  ggplot(aes(x = gender, y = acceptance_rate, fill = gender)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_text(aes(y = 0.05, label = paper_count), size = 3.5, color = "black") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, color = "black", alpha = 0.8) +
  geom_text(aes(x = 1.5, y = 0.89, label = sig), color = "black") +
  geom_segment(aes(x = 1.1, xend = 1.9, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_grid(author_key~composition) +
  coord_cartesian(ylim = c(0.0, 1.0)) +
  theme_dakota() +
  guides(fill = F) +
  labs(y = "% of full submissions accepted",
       x = "Gender of Last Author"
  )

@@

countries_separate <- elife %>%
  filter(full_decision_made & has_full_submission & ca_country %in% countries) %>%
  group_by(ca_country, ca_country_homophily) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_accept_rate = accept_count / paper_count,
    se = 1.96 * sqrt( (encourage_accept_rate * (1 - encourage_accept_rate)) / paper_count),
    lower = encourage_accept_rate - se,
    upper = encourage_accept_rate + se,
    upper = ifelse(upper > 1, 1, upper)
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  left_join(sig_df) %>%
  #top_n(16, totals) %>% # 8 countries, 3 authorship types per country, therefore first 24 rows
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>%
  # Start ggplot
  ggplot(aes(x = ca_country_homophily, y = encourage_accept_rate, fill = ca_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 0.075), size = 2.5) +
  geom_text(aes(label = sig, x = 1.5, y = 0.95)) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap(~ca_country, nrow = 2, ncol = 4) +
  ylim(0, 1) +
  theme_dakota() +
  guides(fill = FALSE) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  labs(
    x = "",
    y = "% of full submissions accepted"
  ) +
  theme(
    axis.text.x = element_text(angle = 20, vjust = 1, hjust = 1)
  )

@@

countries_pooled <- d1.summ %>%
  union(d2.summ) %>%
  union(d3.summ) %>%
  left_join(sig_df, by = "type") %>%
  mutate(type = factor(type, 
                       levels = c("all", "no us", "no founder"),
                       labels = c("All Countries", "No U.S.", "No U.S., U.K., or Germany")
                       )
         ) %>%
  ggplot(aes(x = ca_country_homophily, y = encourage_accept_rate, fill = ca_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 0.10), size = 2.5) +
  geom_text(aes(label = sig, x = 1.5, y = 0.85)) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.8, 1.1), yend = ifelse(sig != "N/A", 0.8, 1.1)), color = "black") +
  facet_wrap(~type, ncol = 3) +
  coord_cartesian(ylim = c(0.0, 1.0)) +
  theme_dakota() +
  guides(fill = FALSE) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  labs(
    x = "",
    y = "% of full submissions accepted"
  ) +
  theme(axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1))

>>>>

# converts a provided p-value into a representation that is easier to visualize
sig2ast <- function(p) { ifelse(p <= 0.0001, "***", 
                                ifelse(p <= 0.001, "***", 
                                       ifelse(p <= 0.01, "**", 
                                              ifelse(p <= 0.05, "*", 
                                                     ifelse(p < 0.1, "-", "ns")
                                              )
                                       )
                                )
                          )
}

@@

# Construct the final plot
gender_homophily <- data_homophily %>% 
  ggplot(aes(x = gender, y = acceptance_rate, fill = gender)) +
  geom_bar(stat = "identity", alpha = 0.8, color = "black") +
  geom_text(aes(y = 0.05, label = paper_count), size = 3.5, color = "black") +
  geom_errorbar(aes(ymin = lower, ymax = upper), width = 0.2, color = "black", alpha = 0.8) +
  geom_text(aes(x = 1.5, y = 0.92, label = sig), size = 4, color = "black") +
  geom_segment(aes(x = 1.1, xend = 1.9, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_grid(author_key~composition) +
  coord_cartesian(ylim = c(0.0, 1.0)) +
  theme_dakota() +
  guides(fill = F) +
  labs(y = "% of full submissions accepted",
       x = "Gender of Last Author",
       title = "A"
  ) +
  theme(plot.title = element_text(size = 20))

@@

countries_separate <- elife %>%
  filter(full_decision_made & has_full_submission & ca_country %in% countries) %>%
  group_by(ca_country, ca_country_homophily) %>%
  summarize(
    paper_count = n(),
    accept_count = sum(accepted == TRUE, na.rm = T),
    encourage_accept_rate = accept_count / paper_count,
    se = 1.96 * sqrt( (encourage_accept_rate * (1 - encourage_accept_rate)) / paper_count),
    lower = encourage_accept_rate - se,
    upper = encourage_accept_rate + se,
    upper = ifelse(upper > 1, 1, upper)
  ) %>%
  group_by(ca_country) %>%
  mutate(totals = sum(paper_count)) %>%
  ungroup() %>%
  left_join(sig_df) %>%
  #top_n(16, totals) %>% # 8 countries, 3 authorship types per country, therefore first 24 rows
  mutate(ca_country = factor(sapply(as.character(ca_country), simpleCap))) %>%
  # Start ggplot
  ggplot(aes(x = ca_country_homophily, y = encourage_accept_rate, fill = ca_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 0.075), size = 2.5) +
  geom_text(aes(label = sig, x = 1.5, y = 0.90), size = 4) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.85, 1.1), yend = ifelse(sig != "N/A", 0.85, 1.1)), color = "black") +
  facet_wrap(~ca_country, nrow = 2, ncol = 4) +
  ylim(0, 1) +
  theme_dakota() +
  guides(fill = FALSE) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  labs(
    x = "",
    y = "% of full submissions accepted",
    title = "C"
  ) +
  theme(
    axis.text.x = element_text(angle = 20, vjust = 1, hjust = 1),
    plot.title = element_text(size = 20)
  )

@@

countries_pooled <- d1.summ %>%
  union(d2.summ) %>%
  union(d3.summ) %>%
  left_join(sig_df, by = "type") %>%
  mutate(type = factor(type, 
                       levels = c("all", "no us", "no founder"),
                       labels = c("All Countries", "No U.S.", "No U.S., U.K., or Germany")
                       )
         ) %>%
  ggplot(aes(x = ca_country_homophily, y = encourage_accept_rate, fill = ca_country_homophily)) +
  geom_bar(stat = "identity", position = position_dodge(), color = "black", alpha = 0.8) +
  geom_errorbar(aes(ymin = lower, ymax = upper), color = "black", width = 0.2) +
  geom_text(aes(label = paper_count, y = 0.10), size = 2.5) +
  geom_text(aes(label = sig, x = 1.5, y = 0.85), size = 4) +
  geom_segment(aes(x = 1, xend = 2, y = ifelse(sig != "N/A", 0.8, 1.1), yend = ifelse(sig != "N/A", 0.8, 1.1)), color = "black") +
  facet_wrap(~type, ncol = 3) +
  coord_cartesian(ylim = c(0.0, 1.0)) +
  theme_dakota() +
  guides(fill = FALSE) +
  scale_fill_brewer(palette = "Oranges", labels = c("No Homogeneity", "Homogeneity")) +
  scale_x_discrete(labels = c("No Homogeneity", "Homogeneity")) +
  labs(
    x = "",
    y = "% of full submissions accepted",
    title = "B"
  ) +
  theme(axis.text.x = element_text(angle = 20, hjust = 1, vjust = 1),
        plot.title = element_text(size = 20))
